\vspace{50pt}\\ \huge \bfseries SKEDGE \\ \vspace{10pt} \Large Smarter course scheduling for our\\ University of Rochester

### 2016-04-13 analytics/usage.tex
random
Fix analytics intro

In this section, I will address many of the features listed in Chapter 2 (Design) and demonstrate their usability. As an overview, since November 3, 2015 (159 days ago), Skedge has seen\ldots

@@

\begin{center}
\begin{tabular}{l}
  \hline
  4,713 users that have added or bookmarked at least one course \\ 
  5,256 schedules, with an average of 5.13 and median of 5 sections per schedule \\ 
  17,124 sessions, 75\% of which are from returning visitors \\ 
  107 sessions averaged per day \\ 
  5.4 pages viewed averaged per session  \\ 
  6 minutes spent averaged per session \\ 
  \hline
\end{tabular}
\end{center}

The figure of 4,713 total users may be a little misleading,

\begin{itemize}
  \item 
\end{itemize}

@@

  \caption{Searches over time, with major relevant calendar events annotated}
  \label{fig:searches}

@@

Figure \ref{fig:searches} shows user search submissions over the time, and makes the periodicity of Skedge usage extremely apparent. Although it only shows a bit more than one ``phase,'' the cycle of events---\emph{semester begins} (students check course times, room locations, etc. while they get accustomed to the semester), \emph{next semester's course catalog released} (students explore the courses offered and build possible schedules), \emph{next semester registration opens} (cross-checking and officially registering each course with the Registrar)---clearly drives the majority of site traffic.

@@

  This already is evidence of an effective search mechanism, but of those empty searches, the vast majority (92\%) contain typos or are for courses that simply don't exist. The other significant portion of searches include instructor names without the requisite ``taught by'' for SkedgeQL to pick it up as an instructor search, and such a fix could easily be made.

>>>>

In this section, I will address many of the features listed in Chapter 2 (Design) and demonstrate their usability. To date, Skedge has seen\ldots

@@

\begin{center}
\begin{tabular}{l}
  \hline
  4,713 users that have added or bookmarked at least one course \\ 
  5,256 schedules, with an average of 5.13 and median of 5 sections per schedule \\ 
  75\% of sessions from returning visitors \\ 
  107 sessions averaged per day \\ 
  5.4 pages viewed averaged per session  \\ 
  6 minutes spent averaged per session \\ 
  \hline
\end{tabular}
\end{center}

\noindent The figure of 4,713 total users may be misleading because, as explained in Chapter 3, if a user resets their browser cookies or changes browsers or devices, this registers as a distinct visitor. Unfortunately, even analytics tools that track unique visitors rely on cookies as well.

In an attempt to exclude ``stale users,'' we can time-constrain our analysis. In the past month, there were 1,416 visitors to the site and 672 visitors \emph{with schedules}. However, this metric excludes data from seniors who did not have need for Skedge in the past month. Going back to November 3, 2015, course registration day ($\sim$5 months ago), we find 4,647 visitors to the site and 1322 visitors with schedules. Thus, we can estimate that the amount of users who have added courses with Skedge is about \textbf{one-fifth} of all undergraduates (6,046) at the College.

@@

  \caption{Searches over the period Oct 19 2015 to Apr 11 2016, annotated with major events}
  \label{fig:searches}

@@

Figure \ref{fig:searches} shows searches over time, and makes the periodicity of Skedge usage extremely apparent. Although there is only enough data for a bit more than one ``phase,'' the cycle of events---\emph{semester begins} (students check course times, room locations, etc. while they get accustomed to the semester), \emph{next semester's course catalog released} (students explore the courses offered and build possible schedules), \emph{next semester registration opens} (cross-checking and officially registering each course with the Registrar)---clearly drives the majority of site traffic.

@@

  This already is evidence of an effective search mechanism, but of those empty searches, the vast majority contain typos or are for courses that simply don't exist. The other significant portion of searches include instructor names without the requisite ``taught by'' for SkedgeQL to pick it up as an instructor search, and this issue could easily be fixed.
